Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-19 intro.tex
titles and notes

>>>>

Notes on wording

 If we define entropy as complexity in the paper (as we do currently) we could say that every signal complicated or not has a balance between temporal/predictive structure and complexity (entropy). So for example, a chaotic signal and a random walk signal are both "complicated" they exhibit interesting behavior (they aren't monotonic, periodic, constant etc.) but one of them is far more complex and less predictable than the other , e.g.,  a random walk or gcc for example is complicated *and* highly complex (very high entropy) where as col is also complicated but not as complex as it exhibits a great deal of predictive structure (low entropy).

An interesting contribution here is that examining a complicated signal (i.e., something that has interesting behavior, not periodic, monotonic, constant etc) of noisy real-valued entries, it is hard to determine a priori (without WPE) where in the spectrum of temporal structure and complexity the signal lies. Is it completely complex and have little to no predictive structure e.g., gcc or is it balanced in complexity and structure like a chaotic signal e.g., col.

One potential issue here is that apparently information theorists say that completely random signals are void of complexity. So Saying that a random walk signal (i.e., a signal with high entropy) is complex may cause some issues. HOWEVER, if we define complexity as entropy I don't think this is an issue.

Ryan does this seem reasonable? Is this an accurate synopsis of our discussion. Please feel free to add to it. Liz do you think making this distinction between "Complicated" and "Complex" would be useful for the readers understanding and dissemination of this topic?

This would suggest changing the title to something a long the lines of "Decoding Complicated Time Series: The balance between complexity and temporal structure and the implications for predictability "
